\documentclass[a4paper,12pt,oneside]{ujbook}
\usepackage{amsmath,amssymb,ascmac,bm}
%\usepackage[dvips]{graphicx}
\usepackage{subfigure}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{thesis}
\usepackage[dvipdfmx]{graphicx}

\begin{document}

\title{
	＜令和元年度専攻科研究論文＞\\
	畳み込み辞書学習を用いた\\クラス分類の検討\\　\\
	指導教官: 黒木祥光 教授\\
	機械・電気システム工学専攻 A3519 平川智也
}
\date{}
\maketitle

\tableofcontents

\chapter{はじめに}
\input{thesis-1.tex}

\chapter{畳み込み辞書学習}
\input{thesis-2.tex}

\chapter{錐制約部分空間法}
\input{thesis-3.tex}

\chapter{提案法}
\input{thesis-4.tex}

\chapter{実験}
\input{thesis-5.tex}

\chapter{むすび}
\input{thesis-6.tex}

\input{thesis-ack.tex}

\begin{thebibliography}{9}
\bibitem{fast-csc}
	Bristow, Hilton, Anders Eriksson, and Simon Lucey，”Fast convolutional sparse coding，”Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2013.
	
\bibitem{super-res}
	Gu, Shuhang, et al. ”Convolutional sparse coding for image super-resolution，” Proceedings of the IEEE International Conference on Computer Vision. 2015.

\bibitem{sub}
	福井和広，”部分空間法の今昔 (いまむかし)(下): 最近の技術動向: 相互部分空間法への拡張とその応用事例，” 情報処理 49.6: 680-685，2008.
	
\bibitem{nmf}
	亀岡弘和，”非負値行列因子分解，” 計測と制御 51.9: 835-844，2012.
	
\bibitem{cone-sub}
	小林匠, and 大津展之，”パターン識別のための錐制約部分空間法，” 電子情報通信学会論文誌 D 92.1: 104-111，2009.
	
\bibitem{optimize-csc}
	Bristow, Hilton, and Simon Lucey，”Optimization methods for convolutional sparse coding，” arXiv preprint arXiv:1406.2407 ，2014.
	
\bibitem{admm}
	Boyd, Stephen, et al，”Distributed optimization and statistical learning via the alternating direction method of multipliers，” Foundations and Trends® in Machine learning 3.1: 1-122，2011.
	
\bibitem{sporco}
	Wohlberg, Brendt，”SPORCO: A Python package for standard and convolutional sparse representations，” Proceedings of the 15th Python in Science Conference, Austin, TX, USA. 2017.

\end{thebibliography}

\end{document}
